% DiBella CV
% LaTeX Curriculum Vitae Template
% 
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
% 
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,letterpaper]{article}

% Essential packages
% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[scale=0.82]{geometry}
\usepackage[T1]{fontenc}
\usepackage{mathpazo} % Palatino font
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage{enumitem}
\setlist[itemize,1]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt, label=\textbullet}
\setlist[itemize,2]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt, label=\textendash}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{booktabs}

% Color definitions
\definecolor{accent}{RGB}{70,130,180} % Steel blue
\definecolor{lightaccent}{RGB}{240,248,255} % Alice blue
\definecolor{linkcolor}{RGB}{0,102,204} % Medium blue

% Hyperref setup
\hypersetup{
    colorlinks = true,
    urlcolor = linkcolor,
    linkcolor = linkcolor,
    citecolor = linkcolor,
    pdfauthor = {Nicholas DiBella},
    pdftitle = {Nicholas DiBella: Curriculum Vitae},
    pdfcreator = {LaTeX}
}

% Page layout
\geometry{
    left=1in,
    right=1in,
    top=0.8in,
    bottom=0.8in,
    footskip=0.5in
}

% Section formatting
\titleformat{\section}{\large\bfseries\scshape\color{accent}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize\thepage}

% Remove paragraph indentation
\setlength{\parindent}{0pt}

% List formatting
\setlist[itemize,1]{leftmargin=*, topsep=0.2ex, partopsep=0ex, parsep=0.5ex, itemsep=0.5ex, label=\textbullet}
\setlist[itemize,2]{leftmargin=2em, topsep=0.1ex, partopsep=0ex, parsep=0.3ex, itemsep=0.3ex, label=\textendash}

\begin{document}

% LaTeX Template Header
% ---
% See original template comments above.

\begin{center}
    {\Large\textsc{Nicholas DiBella}}\\[0.2cm]
\end{center}

\vspace{-0.5cm}

\begin{center}
\begin{tabular}{r l r l}
\textbf{Department of Philosophy} & \hfill & \textbf{Email:} & \href{mailto:dibella@cmu.edu}{dibella@cmu.edu} \\
\href{https://www.cmu.edu/dietrich/philosophy/}{Carnegie Mellon University} & \hfill & \textbf{Website:} & \href{https://nicholasdibella.com}{nicholasdibella.com} \\
Pittsburgh, PA 15213 & \hfill & \textbf{Project:} & \href{https://www.swaybeta.ai}{swaybeta.ai} \\
\end{tabular}
\end{center}

\section*{Areas of Specialization}
AI and Education, Epistemology, Philosophy of Science

\section*{Employment}
\begin{itemize}
    \item Intelligence Community Postdoctoral Research Fellow, Carnegie Mellon University. 2022--Present
    \item Assistant Professor of Philosophy, Bilkent University. 2018--2022
\end{itemize}

\section*{Education}
\begin{itemize}
    \item Ph.D. in Philosophy, Stanford University. 2018.
    \item Visiting Ph.D. Student in Philosophy, Australian National University. Summers 2014--2017.
    \item B.S. in Physics, Minor in Philosophy, Massachusetts Institute of Technology. 2009.
\end{itemize}

\section*{Publications}
\begin{itemize}
    \item 2024. \href{https://read.dukeupress.edu/the-philosophical-review/article-abstract/133/3/223/390918/Cantor-Choice-and-Paradox?redirectedFrom=fulltext}{``Cantor, Choice, and Paradox.''} \emph{The Philosophical Review}, 133(3), 223--263.
    \item 2022. \href{https://www.cambridge.org/core/journals/philosophy-of-science/article/fair-infinite-lotteries-qualitative-probability-and-regularity/88F15215C3FB30BA3C642C95DFB87797}{``Fair Infinite Lotteries, Qualitative Probability, and Regularity.''} \emph{Philosophy of Science}, 89(4), 824--844.
    \item 2018. \href{https://link.springer.com/article/10.1007/s11229-016-1261-3}{``The Qualitative Paradox of Non-Conglomerability.''} \emph{Synthese}, 195(3), 1181--1210.
\end{itemize}

\section*{Selected Presentations}
\begin{itemize}
    \item ``Equipping Students to Dialogue Across Difference'' (with Simon Cullen)
    \begin{itemize}
        \item \href{https://teachinginhighered.com/podcast/equip-students-to-dialog-across-differences-using-an-ai-guide/}{The Teaching in Higher Ed Podcast} (2025)
    \end{itemize}

    \item ``Talk More, Fight Less: How AI Can Help Us Communicate More Effectively, Reason More Rigorously, and Learn to Disagree Constructively'' (with Simon Cullen)
    \begin{itemize}
        \item \href{https://www.youtube.com/watch?v=yenpEKRVaNY&t=1494s}{Bard Center for The Study of Hate}, Bard College (2025)
    \end{itemize}

    \item ``How to Disagree Better'' (with Simon Cullen)
    \begin{itemize}
        \item \href{https://wondros.com/podcast}{The Wondros Podcast} (2025)
    \end{itemize}

    \item ``Harnessing AI to Enhance Constructive Disagreement on Campus'' (with Simon Cullen)
    \begin{itemize}
        \item \href{https://freeexpression.charlotte.edu}{University of North Carolina, Charlotte} (2025)
        \item \href{https://heterodoxacademy.org/events/harnessing-ai-to-enhance-constructive-disagreement-on-campus-hxa-members-only/}{Heterodox Academy workshop} (Aug.\ 2024)
        \item \href{https://www.axim.org/news/ai-education}{Axim Collaborative, AI \& Education Conference} (Oct.\ 2024)
        \item Bard Center for the Study of Hate workshop (Nov.\ 2024)
    \end{itemize}

    \item ``Harnessing AI to Improve Analytic Disagreements''
    \begin{itemize}
        \item Intelligence Community Tech Week (Sept.\ 2024)
    \end{itemize}

    \item ``Promoting Constructive Disagreement and Improving Student Reasoning at Scale'' (with Cullen)
    \begin{itemize}
        \item \href{https://www.thefire.org/get-involved/events/2024-fire-faculty-network-conference}{Foundation for Individual Rights and Expression} (2024)
        \item \href{https://www.axim.org/news/ai-education}{Axim Collaborative, AI \& Education} (2024)
        \item Bard Center for The Study of Hate (2024)
    \end{itemize}

    \item ``Structured Reasoning Techniques to Improve Intelligence Products and Interagency Communication'' (with Simon Cullen)
    \begin{itemize}
        \item Presentations to NSA, IARPA, CIA, and U.S. Senate Intel Staffers (2023)
    \end{itemize}

    \item ``Visual Strategies to Improve Group Reasoning, Policymaking, and Understanding Across the Aisle'' (with Simon Cullen)
    \begin{itemize}
        \item \href{https://bipartisanpolicy.org}{Bipartisan Policy Center} (2023)
    \end{itemize}
\end{itemize}

\section*{Grants \& Funding}
\begin{itemize}
    \item \href{https://tools-competition.org/25-winners-press-release/}{Learning Agency Tools Competition Growth-Level Prize}, with Simon Cullen. (\$150,000, 2025)
    \item \href{https://www.avdf.org/}{Arthur Vining Davis Foundations grant} for Sway (AI-scaffolded chat platform), with Simon Cullen. (\$35,000, 2024)
    \item \href{https://givingpledge.org/pledger?pledgerId=383}{Ben Delo Foundation research grant}, with Simon Cullen. (\$37,500, 2024)
    \item \href{https://www.library.cmu.edu/about/news/2024-07/ofai}{Omidyar Network/Open Forum for AI research grant}, with Simon Cullen. (\$50,000, 2024)
    \item \href{http://www.sniderfoundation.org}{Snider Foundation research grant}, with Simon Cullen. (\$50,000, 2025)
    \item \href{https://orise.orau.gov/icpostdoc/index.html}{Intelligence Community Postdoctoral Research Fellowship Program}, ``Probabilistic Visualization of Complex Arguments to Resolve Analytic Disagreements.'' U.S. Office of the Director of National Intelligence and U.S. Department of Energy: ICPD-2022-08. Advised by Simon Cullen and Steve Rieber. (\$297,000, 2022--2025)
\end{itemize}

\section*{Awards \& Honors}
\begin{itemize}
    \item \href{https://tools-competition.org/25-winners-press-release/}{Tools Competition Winner}, with Simon Cullen, 2025
    \item Mellon Foundation Dissertation Fellowship, 2017--2018
    \item Eastern APA Graduate Student Travel Stipend, 2017
    \item Patrick Suppes Fellowship in Philosophy of Science, 2010--2015
    \item MIT Class of 1946 Scholarship, 2007--2009
\end{itemize}

\section*{Teaching Experience}
\subsection*{Primary Instructor, Bilkent University}
\begin{itemize}
    \item Paradox and Infinity (Fall 2019, Fall 2020, Fall 2021)
    \item Social and Political Philosophy II (Spring 2019, Spring 2020, Fall 2021)
    \item Social and Political Philosophy I (Fall 2018, Fall 2019, Fall 2020)
\end{itemize}

\subsection*{Teaching Assistant, Stanford University}
\begin{itemize}
    \item Thinking about the Universe (Spring 2018)
    \item Introduction to Philosophy (Spring 2017)
    \item Introduction to Moral Philosophy (Winter 2017)
    \item Metaphysics (Spring 2016)
    \item Survey of Formal Methods (Fall 2015)
    \item Existentialism (Spring 2014)
    \item Philosophy and Literature (Winter 2014)
    \item Mind, Matter, and Meaning (Fall 2012, Spring 2013)
    \item Introductory Logic (Fall 2011)
\end{itemize}

\subsection*{MIT Educational Studies Program, 2007--2009}
\begin{itemize}
    \item \textit{The Big Questions} (2008). Published at ocw.mit.edu/high-school/physics/the-big-questions/ with video lectures and notes.
    \item \textit{Excitatory Topics in Physics} (2007). Published at ocw.mit.edu/high-school/physics/excitatory-topics-in-physics/ with video lectures and notes.
\end{itemize}

\section*{Service \& Professional Activities}
\begin{itemize}
    \item \textbf{Journal Referee:} \textit{Analysis}, \textit{Canadian Journal of Philosophy}, \textit{Ergo}, \textit{Erkenntnis}, \textit{European Journal for Philosophy of Science}, \textit{International Studies in the Philosophy of Science}, \textit{Pacific Philosophical Quarterly}, \textit{Philosophia Mathematica}, \textit{Philosophical Quarterly}, \textit{Philosophy of Science}, and \textit{Synthese}.
    \item \textbf{Graduate-Student Editor:} \textit{The Dualist}, Stanford's undergraduate philosophy journal, 2013--2016.
\end{itemize}

\section*{References}
\begin{tabular}{ll ll}
\textbf{Ray Briggs} & & \textbf{Kenny Easwaran} \\
Professor of Philosophy & & Associate Professor of Philosophy \\
University of Chicago & & University of California, Irvine \\
rabriggs@uchicago.edu & & k.easwaran@uci.edu \\
\\
\textbf{Alan Hájek} & & \textbf{Mark Crimmins} \\
Professor of Philosophy & & Associate Professor of Philosophy \\
Australian National University & & Stanford University \\
hajek.alan@gmail.com & & crimmins@stanford.edu \\
\end{tabular}

% Footer with last updated date (commented)
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}